
%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt]{article} % Font size, can be: 10pt, 11pt or 12pt

\input{structure.tex} % Include the file that specifies the document structure

\begin{document}

\begin{paracol}{2} % Begin the multi-column environment

%----------------------------------------------------------------------------------------
%	NAME AND CURRICULUM VITAE TEXT
%----------------------------------------------------------------------------------------

\parbox[top][0.06\textheight][c]{\linewidth}{ % Parbox to hold the author name and CV text; fixed height to match the coloured box to the right, centred vertically and full line width
	\vspace{-0.04\textheight} % Reduce whitespace above the parbox to separate it from the main content
	\centering % Centre text
	{\sffamily\Huge Anna Novoseltseva}\\\medskip % Your name
}

%----------------------------------------------------------------------------------------
%	MAJOR RESEARCH PROJECT
%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\section{Education} 

%------------------------------------------------

\begin{supertabular}{rl} % Start a table with two columns, the table will ensure everything is aligned

	\educationentry{2016-2018} % Duration
	{Master of Science} % Degree
	{GPA: 3.9/4.0} % Honours, achievements or distinctions (e.g. first class honours)
	{Biomedical Engineering} % Department
	{Worcester Polytechnic Institute} % Institution
	
	%------------------------------------------------
	
	\educationentry{2011 -- 2015} % Duration
	{Bachelor of Science} % Degree
	{GPA: 4.8/5.0} % Honours, achievements or distinctions (e.g. first class honours)
	{Biotechnical Systems and Technologies} % Department
	{Tomsk Polytechnic University} % Institution
	
	%------------------------------------------------

\end{supertabular}

\section{Research Experience}

\workposition{JAN 2017 - AUG 2018} % Duration
{} % FT/PT (full time or part time)
{Worcester Polytechnic Institute, Worcester, MA, USA} % Employer
{Master`s thesis} % Job title
{Designed, prototyped, and tested a three-axis force measurement device for the da Vinci surgical system to provide haptic feedback to the operator based on forces applied to the instruments. Designed electronics and analog control circuits. Developed a ROS package to interface with the da Vinci Research Kit.} % Description

%------------------------------------------------

\workposition{AUG 2014 – DEC 2016} % Duration
{}
{Tomsk Polytechnic University, Tomsk, Russian Federation} % Employer
{Bachelor`s thesis} % Job title
{Designed and developed electronic circuits of
a device for determining the location of hematomas
using infrared spectroscopy. Programmed STM32 microcontroller
in C for device control. Created
a program for data analysis and acquisition using
LabVIEW. Implemented RS232 serial communications
between PC and developed device.}  % Description

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE
%----------------------------------------------------------------------------------------

\section{Professional Experience}

% Blank \workposition command to add another job:
%------------------------------------------------

\workposition{Current, from Sept 2018} % Duration
{FT} % FT/PT (full time or part time)
{NTO IRE Polus, Fryazino, Russian Federation} % Employer
{Engineer} % Job title
{Designed and implemented the commercial-scale manufacturing process for a new medical laser treatment product. Responsible for component quality assurance, inventory database development, and design of assembly line process equipment.} % Description

%------------------------------------------------

\workposition{Summer 2017, 2018} % Duration
{FT} % FT/PT (full time or part time)
{IPG Medical, Marlborough, MA, USA} % Employer
{Internship} % Job title
{Research, development, and testing of new medical laser system for dermatology. Conducted laser-tissue interaction experiments with biological tissue samples and phantoms.}  % Description

%------------------------------------------------

\workposition{Summer 2014} % Duration
{PT} % FT/PT (full time or part time)
{Medtekhnika, Ulan-Ude, Russian Federation} % Employer
{Internship} % Job title
{Assisted in technical support and repair of medical equipment in hospitals and clinics.} % Description

%------------------------------------------------

\vspace{-\baselineskip}\medskip % Standardise the whitespace after this section and before the next (the custom command adds too much otherwise)

\switchcolumn % Switch to the next paracol column

%----------------------------------------------------------------------------------------
%	COLOURED CONTACT DETAILS BOX
%----------------------------------------------------------------------------------------

\parbox[top][0.06\textheight][c]{\linewidth}{ % Parbox to hold the colour box; fixed height to match the name/CV text to the left, centred vertically and full line width
	\vspace{-0.04\textheight} % Reduce whitespace above the parbox to separate it from the main content
	\colorbox{shade}{ % Create the coloured box
		\begin{supertabular}{p{0.05\linewidth}|p{0.775\linewidth}} % Start a table with two columns, the table will ensure everything is aligned
			\raisebox{-1pt}{\faPhone} & +7 (926) 963-7569 \\ % Phone number
			\raisebox{0pt}{\small\faEnvelope} & \href{mailto:anovoseltseva@wpi.edu}{anovoseltseva@wpi.edu} \\ 
		\end{supertabular}
	}
}

%----------------------------------------------------------------------------------------
%	AWARDS
%----------------------------------------------------------------------------------------

\section{Awards}

% Example \tableentry{} command to add another line:

%\tableentry{Heading}{Content}{spaceafter}

% All 3 parameters must be supplied but any can be empty if you don't need them
% A "spaceafter" value in the third parameter will add some vertical space -- this is to be used between headings

%------------------------------------------------
\begin{supertabular}{rl} % Start a table with two columns, the table will ensure everything is aligned
	
	%------------------------------------------------
	
	\tableentry{2016 - 2018}{Fulbright Scholarship}{spaceafter}
	
	%------------------------------------------------
	
	\tableentry{2015}{1\textsuperscript{st}-place team in All-Russian Student}{}
	\tableentry{}{Competition on Electronics}{spaceafter}

	%------------------------------------------------
	\tableentry{2015}{Certificate of research achievements}{}
	\tableentry{}{\textit{Tomsk Polytechnic University}}{spaceafter}
	
	\tableentry{2014}{1\textsuperscript{st}-place team in the regional stage in}
	{}
	\tableentry{}{All-Russian Student Competition on}{}
	{}
	\tableentry{}{Electronics}{spaceafter}

	%------------------------------------------------
	
\end{supertabular}

%	COMPUTER SKILLS
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%	COMMUNICATION SKILLS
%----------------------------------------------------------------------------------------

\section{Presentations}

%------------------------------------------------
\longformpublication{IV International Forum for Young Scientists \\”Space Engineering" (2016)}

\longformpublication{II International Scientific Conference Foreign \\Languages in the Context of the Professional \\Communication Problems (2016)}

\longformpublication{XXI International Scientific Conference (STT 2015) \\ for students and scientists "Modern Equipment and \\ Technologies" (2015)}

%----------------------------------------------------------------------------------------
%	SKILLS DESCRIPTION
%----------------------------------------------------------------------------------------

\section{Skills}

% Example \longformdescription{} command to add another section:

%\longformdescription{Heading}{Description}

%------------------------------------------------

\longformdescription{Programming Languages}{C \textbullet{} Matlab \textbullet{} Python \textbullet{} ROS \textbullet{}  \LaTeX \textbullet{} Visual Basic \textbullet{} C\#}

\longformdescription{Software}{Altium Designer • SolidWorks
 • MathCAD • LabVIEW \\ IAR Embedded Workbench • Keil MDK}

\longformdescription{Additional Skills}{ • Circuit board and PCB soldering \\ • Electronic circuit design \\ • Machine component design \\• Programming of microcontrollers}


%----------------------------------------------------------------------------------------
%	REFERENCES
%----------------------------------------------------------------------------------------

\section{References}

\begin{supertabular}{rl} % Start a table with two columns, the table will ensure everything is aligned
	
% 	%------------------------------------------------
	
 	\tableentry{}{\textbf{Dr. Gregory S. Fischer}}{spaceafter}
 	\tableentry{Position}{Professor}{}
 	\tableentry{Employer}{\href{https://www.wpi.edu/people/faculty/gfischer}{Department of Mechanical Engineering}}{}
 	\tableentry{}{\href{https://www.wpi.edu}{\textit{Worcester Polytechnic Institute}}}{spaceafter}
 	\tableentry{Email}{\href{mailto:gfischer@wpi.edu}{gfischer@wpi.edu}}{}
 	\tableentry{Phone}{+1 (508) 831-5261 (Work)}{}
	
% 	%------------------------------------------------
	
 	\tableentry{}{}{} % Creates some additional whitespace between the references
	
% 	%------------------------------------------------
	
 	\tableentry{}{\textbf{Dr. Ilya Yaroslavsky}}{spaceafter}
 	\tableentry{Position}{Manager of Advanced Product Development}{}
 	\tableentry{Employer}{\href{https://www.ipgphotonics.com/}{IPG Medical}}{spaceafter}
 	\tableentry{Email}{\href{mailto:iyaroslavsky@ipgphotonics.com}{iyaroslavsky@ipgphotonics.com}}{}
 	\tableentry{Phone}{+1 (508) 373-1100 (Work)}{}
	
% 	%------------------------------------------------
	
 \end{supertabular}

 \medskip % Extra whitespace before the next section

%
%----------------------------------------------------------------------------------------

\end{paracol}

%----------------------------------------------------------------------------------------
%	PUBLICATIONS
%----------------------------------------------------------------------------------------

\section{Publications}

% Example \longformdescription{} command to add another publication:

%\longformpublication{Reference (format this manually as desired)}

%------------------------------------------------
\longformpublication{\textbf{Novoseltseva A.} (2018). "Force Feedback for the Patient Side Manipulator of the daVinci Research Kit", \textit{Masters Theses (All Theses, All Years)}, 312, https://digitalcommons.wpi.edu/etd-theses/312 }

\longformpublication{Yaroslavsky I., Vinnichenko V., McNeill T., \textbf{Novoseltseva A.}, Perchuk I., Vybornov A., Altshuler G., Gapontsev V. (2018). "Optimization of a novel Tm fiber laser lithotripter in terms of stone ablation efficiency and retropulsion reduction" \textit{Proc. SPIE 10468, Therapeutics and Diagnostics in Urology 2018}, 104680H doi: 10.1117/12.2291089;} 

\longformpublication{Erakhtin I., Aristov A., \textbf{Novoseltseva A.}, Sukhanov V. (2017). "Design of optoelectronic system for optical diffusion tomography" \textit{V International Forum for Young Scientists "Space Engineering"}, DOI: 10.1051;} 

\longformpublication{\textbf{Novoseltseva A.}, Aristov A., Timchenko K. (2016). Experimental Facility Control System for Optical Studies in the Frame of Problem Solving of Brain Hematoma Diagnostics, \textit{IOP Conference Series: Materials Science and Engineering,}, Vol 93, No 012002, pp 1-5.}

\longformpublication{\textbf{Novoseltseva A.}, Musorov I., Torgaev S., Aristov A., (2016). The Control System of the Opotoelectronic Sensor, \textit{IV International
Forum for Young Scientists ”Space Engineering”}, pp 262-265.}

\longformpublication{Aristov A., Timchenko K., \textbf{Novoseltseva A.}, Kustov D., Larioshina I., (2016). Designing of Phantom Head Used in Optical Diagnostics of Brain Injury, \textit{Journal of Physics: Conference Series}, Vol 671, No 012002, pp 1-5.}

\longformpublication{Timchenko K., \textbf{Novoseltseva A.}, Aristov A., (2016). Research of the Methods for Reading Optical Density on Different Parts of Human Head, \textit{IV International Forum for Young Scientists ”Space Engineering”},pp 272-277}

\longformpublication{Timchenko K, \textbf{Novoseltseva A}, Aristov A, (2015). Designing of Phantom Head for Conducting Optical Researches, \textit{Atomic and molecular pulsed lasers : The 12th International Conference},pp 132}

%------------------------------------------------

%----------------------------------------------------------------------------------------

\end{document}
